A thesis draft

### 2018-11-29 res/sections/08-Background.tex
Fix citation in background

Part of the new requirements can be satisfied using a large radio spectrum with
higher frequencies. The utilization of higher frequencies, though, mean that the
radio signals can be easily disrupted by physical objects, like buildings and
many geographical elements (such as hills and mountains), clashing with the
expectation of an ever-reachable connectivity. It is here where virtualization
plays an important role. In fact, the re-design of some network components today
existing via hardware can transform a monolithic networking approach to a 
modular one, exploiting the flexibility that Virtual Network Functions 
(VNFs)\cite{moens2014vnf} can offer thanks to virtualization, closing the gap to
the use-case fulfillment defined by the NGMN alliance~\cite{iwamura2015ngmn}
which require a decreased time to set up and deploy network services
(specifically, from 90 hours to 90 minutes~\cite{networld20202014role}).

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.2]{networkslicing}
  \caption[The three layers model of network slicing]{The three layers model of
    network slicing~\cite{alliance2016description}}
  \label{chap:background:img:network_slicing}
\end{figure}

>>>>

Part of the new requirements can be satisfied using a large radio spectrum with
higher frequencies. The utilization of higher frequencies, though, mean that the
radio signals can be easily disrupted by physical objects, like buildings and
many geographical elements (such as hills and mountains), clashing with the
expectation of an ever-reachable connectivity. It is here where virtualization
plays an important role. In fact, the re-design of some network components today
existing via hardware can transform a monolithic networking approach to a
modular one, exploiting the flexibility that Virtual Network Functions
(VNFs)~\cite{moens2014vnf} can offer thanks to virtualization, closing the gap
to the use-case fulfillment defined by the NGMN alliance~\cite{iwamura2015ngmn}
which require a decreased time to set up and deploy network services
(specifically, from 90 hours to 90 minutes~\cite{networld20202014role}).

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.3]{networkslicing}
  \caption[The three layers model of network slicing]{The three layers model of
    network slicing~\cite{alliance2016description}}
  \label{chap:background:img:network_slicing}
\end{figure}
